---
title: "Some Report on Sentencing and Stuff"
author: "Tom Hanks"
date: "13/11/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

<!-- Let's first read in our dataset and get some key values -->
```{r echo = FALSE, results='hide', message=FALSE}
library(dplyr)
library(ggplot2)
per <- function(num,den){ round(100*num/den)}
s3tools::get_credentials()
col_types = readr::cols(
    year = readr::col_integer(),
    offence_group = readr::col_character(),
    sentenced = readr::col_integer(),
    count = readr::col_integer()
)
sentencing_data <- aws.s3::s3read_using(readr::read_csv, col_types = col_types, object = 'simple_data/simple_sentencing_data.csv', bucket = 'alpha-everyone')
sentencing_data$count2 <- sentencing_data$count
latest_year <- 2016
p_5 <- latest_year - 5
p_10 <- latest_year - 10

# Get some headline values
total_latest_appear <- sum(sentencing_data[sentencing_data$year == latest_year, 'count'])
total_latest_sent <- sum(sentencing_data[sentencing_data$year == latest_year & sentencing_data$sentenced == 1, 'count'])
total_p10_appear <- sum(sentencing_data[sentencing_data$year == p_10, 'count'])
total_p10_sent <- sum(sentencing_data[sentencing_data$year == p_10 & sentencing_data$sentenced == 1, 'count'])

```

# Sentencing Report
In `r latest_year` there were `r total_latest_appear` defendants who appeared at court of which `r total_latest_sent` were sentenced (`r per(total_latest_sent, total_latest_appear)`%). The number of defendants sentenced has changed by `r per(total_latest_sent, total_p10_sent) - 100`% from 10 years ago when the number of defendants sentenced was `r total_p10_sent`.

```{r, echo=FALSE}
year_data <- sentencing_data %>% group_by(year) %>% summarise(count = sum(count))
ggplot(data=year_data, aes(x=year, y=count)) + geom_line() + geom_point() + expand_limits(y = 0) + theme_bw()
```

# Branch text
Here is some new work on the branch

# Collaboration
Some text for sam to work on made by jon

# Controversial opinion
Andy Poulton's code is the best!

